%!TEX root =cv.tex
\begin{rubric}{}
%
%
%
%
%
%
\subrubric{Scientific Communications}
\br\ms
\entry*
\hspace{-2ex}\usefont{T1}{phv}{m}{n}\selectfont\textit{\textbf{\large Peer
Reviewed articles}}
%
%
\entry*[$\boldsymbol{2015}$]%
- "Prediction of required MgO volumic fraction in ADS fuel dedicated to minor
actinides transmutation", \textbf{N.~Thiollière, F.~Courtin, B.~Leniau,
  B.~Mouginot \textit{et al.}}, \textit{Progress in Nuclear Energy}, 85, (2015).
%
%
 \entry*[$\boldsymbol{2015}$]%
- "MOX fuel enrichment prediction in PWR using polynomial models",
\textbf{B.~Mouginot, B.~Leniau, T.~Thiolière \textit{et al.}}, \textit{Annals of
Nuclear Energy}, 85, (2015).
%
%
 \entry*[$\boldsymbol{2015}$]%
- "A neural network approach for burn-up calculation and its application to the
dynamic fuel cycle code CLASS", \textbf{B.~Leniau, B.~Mouginot, T.~Thiolière
  \textit{et al.}}, \textit{Annals of Nuclear Energy}, 81, (2015).
%
%
 \entry*[$\boldsymbol{2014}$]%
- "Advanced plutonium management in PWR, complementarity of thorium and uranium",
\textbf{M.~Ernoult \textit{et al.}}, \textit{Progress in Nuclear Energy}, 78,
(2014).
%
%
 \entry*[$\boldsymbol{2013}$]%
- "Structure of $^{80}$Ge revealed by the $\beta$ decay of isomeric states in
$^{80}$Ga: Triaxiality in the vicinity of $^{78}$Ni", \textbf{D.~Verney,
  B.~Tastet \textit{et al.}}, \textit{Physical Review C}, 87, (2013).
%
%
\entry*[$\boldsymbol{2012}$]%
- "Lifetime measurement of 2+1 state in $^{74}$Zn by differential plunger method",
\textbf{M.~Niikura, ~~~~~~B.~Mouginot \textit{et al.}}, \textit{Physical Review
C}, 85, (2012).
%
%
\entry*[$\boldsymbol{2012}$]%
- "First g(2$^{+}$) measurement on neutron-rich $^{72}$Zn, and the high-velocity
transient field technique for radioactive heavy-ion beams", \textbf{E.~Fiori
  \textit{et al.}}, \textit{Physical Review C}, 85, (2012).
%
%
\entry*[$\boldsymbol{2012}$]%
- "Low-lying neutron \textit{fp}-shell intruder states in $^{27}$Ne",
\textbf{S.M.~Brown, W. N.~Catford, J.S.~Thomas ~~~~~~~\textit{et al.}},
\textit{Physical Review C}, 85, (2012).
%
%
 \entry*[$\boldsymbol{2012}$]%
- "Structure of the N=50 As, Ge, Ga nuclei", \textbf{E.~Sahin \textit{et al.}},
\textit{Nuclear Physics A}, 893, (2012).
%
%
%
\entry*[$\boldsymbol{2011}$]%
- "Emergence of the N = 16 shell gap in $^{21}$O", \textbf{B.~Fernandez-Dominguez,
  J.S.~Thomas \textit{et al.}}, \textit{Physical Review C}, 84, (2011).
%
%
\entry*[$\boldsymbol{2011}$]%
- "Search for the giant pairing vibration through (p,t) reactions around 50 and 60
MeV", ~~~~~~~~~~\textbf{B.~Mouginot, E.~Khan, N.~Retief \textit{et al.}},
\textit{Physical Review C}, 83, (2011).
%
%
%
\entry*[$\boldsymbol{2009}$]%
- "Experimental study of $^{84}$Ga $\beta$ decay: Evidence for a rapid onset of
collectivity in the vicinity of $^{78}$Ni", \textbf{M.~Lebois, D.~Verney,
  F.~Ibrahim, S.~Essabaa \textit{et al.}}, \textit{Physical Review C}, 80,
  (2009).
%
%
\entry*[$\boldsymbol{2009}$]%
- "Study of the $^{20}$O(d,t) Reaction with the TIARA-MUST2-VAMOS-EXOGAM Setup",
\textbf{A.~Ramus ~~~~~~\textit{et al.}}, \textit{International Journal of Modern
Physics E}, (2009).
%
\entry*[$\boldsymbol{2009}$]%
- "Structure of the Neutron Rich Ga and Ge Isotopes Observed at Alto",
\textbf{D.~Verney, M.~Lebois, F.~Ibrahim, S.~Essabaa \textit{et al.}},
\textit{International Journal of Modern Physics E}, (2009).
%
%
%
\vspace{0.5cm}
%
%
%
\entry*%
\hspace{-2ex}\usefont{T1}{phv}{m}{n}\selectfont\textit{\textbf{\large Conference Proceedings}}
\entry*[$\boldsymbol{2017}$]%
- "An Integrated Nuclear Archaeology Approach to Reconstructing Fissile Material
Production Histories", \textbf{M.~G\"{o}ttsche, B.~Mouginot \textit{et al.}},
\textit{ESDRA 2017}, Düsseldorf, Germany (2017).
%
%
%
\entry*[$\boldsymbol{2015}$]%
- "Mean Cross Section Prediction in PWR-MOX Using Neural Network "
\textbf{B.~Leniau, B.~Mouginot, N.~Thiolière \textit{et al.}}, \textit{GLOBAL
2015}, Paris, France (2015).
%
\entry*[$\boldsymbol{2015}$]%
- "ADS Fuel Loading Model for Minor Actinides Transmutation Scenarios "
\textbf{N.~Thiolière, F.~Courtin, B.~Mouginot, B.~Leniau \textit{et al.}},
\textit{GLOBAL 2015}, Paris, France (2015).
%
%
%
\entry*[$\boldsymbol{2014}$]%
- "Core Library Advanced Scenario Simulation, Principle \& Application."
\textbf{B.~Mouginot, B.~Leniau, N.~Thiolière \textit{et al.}}, \textit{PHYSOR
2014}, Kyoto, Japon (2014).
%
%
%
 \entry*[$\boldsymbol{2013}$]%
 "CLASS: Core Library for Advanced Scenario Simulation." \textbf{B.~Mouginot,
 N.~Thiolière}, ~~~~~~~~~\textit{TCADS 2}, Nantes, France (2013).
%
\entry*[$\boldsymbol{2013}$]%
 "A high power ADS concept for the minor actinides transmutation."
 \textbf{N.~Thiolière, B.~Mouginot, J.B.~Clavel}, \textit{TCADS 2}, Nantes,
 France (2013).
%
%
%
 \entry*[$\boldsymbol{2010}$]%
- "Lifetime measurement of $2^+_1$ state in $^{74}$Zn with differential Plunger
technique", \textbf{M.~Niikura, B.~Mouginot \textit{et al.}},\textit{XLV
Zakopane Conference on Nuclear physics} "Extremes of the Nuclear Landscape",
Zakopane, Pologne (2010).
%
\entry*[$\boldsymbol{2010}$]%
- "Lifetime measurement of $2^+_1$ state in $^{74}$Zn with differential Plunger
technique", \textbf{M.~Niikura, B.~Mouginot \textit{et al.}}, \textit{11th
Symposium on Nuclei in the Cosmos}, Heidelberg, Allemagne (2010).
%
\entry*[$\boldsymbol{2010}$]%
- "Spectroscopic study of $^{26}$Si for application to nova gamma-ray emission",
\textbf{N.~de~Séréville \textit{et al.}}, \textit{FINUSTAR3}, Rhodes, Grèce
(2010).
%
\entry*[$\boldsymbol{2010}$]%
- "Spectroscopic study of $^{26}$Si for application to nova gamma-ray emission",
\textbf{N.~de~Séréville \textit{et al.}}, \textit{NIC XI}, Heidelberg, Allemagne
(2010).
%
%
%
\entry*[$\boldsymbol{2009}$]%
- "Probing High-Velocity Transient-Field Strength Using Heavy-ions Traversing Fe
and Gd", \textbf{E.~Fiori, G.~Georgiev, A.~E. Stuchbery, A.~Jungclaus,
  \textit{et al.}}, \textit{Nuclear Structure and Dynamics}, Dubrovnik, Croatia
  (2009).
%
\entry*[$\boldsymbol{2009}$]%
- "Magnetic moment of the 2+ state in the neutron-rich radioactive $^{72}$Zn using
the High-Velocity Transient-Field technique", \textbf{E.~Fiori, G.~Georgiev,
  A.~E. Stuchbery, A.~Jungclaus, \textit{et al.}}, \textit{Nuclear Structure and
  Dynamics}, Dubrovnik, Croatia (2009).
%
\entry*[$\boldsymbol{2009}$]%
- "Does transfer confirm knockout results for spectroscopic factor suppression
with radioactive beams?", \textbf{J.S.~Thomas \textit{et al.}}, \textit{Nuclear
Structure and Dynamics}, Dubrovnik, Croatia (2009).
%
%
%
\entry*[$\boldsymbol{2008}$]%
- "Structure of the neutron rich Ga and Ge isotopes observed at Alto",
\textbf{M.~Lebois, D.~Verney, F.~Ibrahim, S.~Essabaa \textit{et al.}},
\textit{Japanese French Symposium - New paradigms in Nuclear Physics}, Paris,
France (2008).
%
\entry*[$\boldsymbol{2008}$]%
- "Study of the $^{20}$O(d,t) reaction with the TIARA-MUST2-VAMOS-EXOGAM setup",
\textbf{A.~Ramus ~~~~~~\textit{et al.}}, \textit{Japanese French Symposium - New
paradigms in Nuclear Physics}, Paris, France (2008).  %
%
%
%
\vspace{0.5cm}
%
%
%
\entry*%
\hspace{-2ex}\usefont{T1}{phv}{m}{n}\selectfont\textit{\textbf{\large Workshops/Conferences}}
%
\entry*[$\boldsymbol{2016}$]%
- "Impact of Isotope Fidelity on Fuel Cycle Calculations" \textbf{B.~Mouginot,
P.P.H.~Wilson, R.W.~Carlsen}, \textit{Winter ANS 2016}, Las Vegas, U.S.A (11/2016) : oral presentation.
%
%
%
\entry*[$\boldsymbol{2016}$]%
- "Transition Analysis with Cyclus" \textbf{B.~Mouginot \textit{et al.}}, \textit{Dynamic Nuclear
Fuel Cycle Workshop}, Paris, France (2016): oral presentation.
%
%
%
\entry*[$\boldsymbol{2015}$]%
- "CLASS Overview" \textbf{B.~Mouginot}, \textit{CLASS/CYCLUS Workshop}, Madison,
Wisonsin, USA  (2015): oral presentation.
%
\entry*[$\boldsymbol{2015}$]%
- "French Fleet Application" \textbf{B.~Mouginot}, \textit{CLASS/CYCLUS Workshop},
Madison, Wisconsin, USA (2015): oral presentation.
%
%
%
\entry*[$\boldsymbol{2012}$]%
- "CLASS, a New Tool for Nuclear Scenarios" \textbf{B.~Mouginot, J.B.~Clavel and
N.~Thiolière}, \textit{International Conference on Nuclear Power Engineering},
Madrid, Spain (2012): poster.
%
%
%
\entry*[$\boldsymbol{2010}$]%
- "Exploring life-time of low-lying states in neutron rich nuclei towards
$^{78}$Ni with the plunger technique at GANIL", \textbf{B.~Mouginot, M.~Niikura
  \textit{et al.}}, \textit{EURORIB'10}, Lamoura, France (2010): oral presentation.
%
%
%
\entry*[$\boldsymbol{2008}$]%
- "Giant pairing vibrations: experimental overview", \textbf{B.~Mouginot, E.~Khan,
  R.~Neveling \textit{et al.}}, \textit{Probing pair correlations Experimental
  tools and associated models, Workshop}, Saclay, France (2008): oral presentation.
%
\entry*[$\boldsymbol{2008}$]%
- "Search of the Giant Pairing Vibration mode in nuclei", \textbf{B.~Mouginot,
  E.~Khan, R.~Neveling ~~~~~~~~~~~~\textit{et al.}}, \textit{LEA COLLIGA
  Meeting}, Catane, Italy (2008): oral presentation.
%
%
%
%
%
%
\end{rubric}

