%!TEX root =cv.tex
\begin{rubric}{}
%
%
%
%
%
\subrubric{Education}
\br
\ms
\entry*[$\boldsymbol{10/2007}$ - $\boldsymbol{12/2010}$]%
\textbf{Ph.D in Sciences, University of Paris XI, France}, "\textit{Search for Giant Pairing Vibration} \& \textit{Life time measurement using PLUNGER method in $^{74}$Zn}".
\entry*[$\boldsymbol{2004}$ - $\boldsymbol{2007}$]%
\textbf{MASTER DEGREE in Nuclei, Particles, Astro-Particles and Cosmology, University of Paris XI}.
\vspace{0.1cm}
%
%
%
%
%
\subrubric{Professional Experiences}
\br\ms
\entry*[$\boldsymbol{10/2015}$ - present ]%
\textbf{Assistant Visiting Scientist, Department of Nuclear Engineering,  University of
Wisconsin-Madison}, "\textit{Electro-nuclear systems and dynamic fuel cycle
calculations}": developement of Cyclus fuel cycle tool, analyzed scenarios in
support of Fuel Cycle Option campaign, fuel fabrication and cross section prediction
models.
\entry*[$\boldsymbol{08/2012}$ - $\boldsymbol{07/2015}$]%
\textbf{Scientist, Subatech, Nantes (FRANCE)}, "\textit{Electro-nuclear systems
and dynamic fuel cycle calculations}" : development of CLASS, a dynamic fuel
cycle simulations software, fuel fabrication and cross section prediction
models, fuel cycle calculations.
\entry*[$\boldsymbol{08/2011}$ - $\boldsymbol{07/2012}$]%
\textbf{Postdoctoral position, Subatech}, "\textit{Electro-nuclear systems and dynamic fuel cycle calculations}".
\entry*[$\boldsymbol{10/2007}$ - $\boldsymbol{12/2010}$]%
\textbf{Research Assitant, Institut de Physique Nucléaire d'Orsay}, "\textit{Search for Giant Pairing Vibration} \& \textit{Life time measurement using PLUNGER method in $^{74}$Zn} : $\gamma$ and mass spectroscopy, data analysis, C/C++ development.
\vspace{0.1cm}
%
%
%
%
%
\subrubric{Teaching}
\br\ms
\entry*[$\boldsymbol{2011/2014}$]%
\textbf{Lecturer in calculus of variations, Ecole des Mines de Nantes (EMN)}, 3$\times$12h.
\entry*[$\boldsymbol{2011/2014}$]%
\textbf{Projects supervision, EMN}, 2$\times$20h \& 3$\times$23h.
\entry*[$\boldsymbol{2011/2013}$]%
\textbf{Laboratory Instructor of Analog electronics, EMN}, 2$\times$18h.
\entry*[$\boldsymbol{2013}$]%
\textbf{Master 2 Intership supervision, EMN}, 6 months.
\entry*[$\boldsymbol{2012}$]%
\textbf{Master I Intership supervision, EMN}, 7 weeks.
\vspace{0.2cm}
%
%
%
%
%
\subrubric{Skills}
\br\ms
\entry*[Simulation]%
LISE++, SRIM, Geant4, MCNP/MCNPX, MURE, CLASS, Cyclus.
\entry*[Software Development]%
C/C++, Shell Script, Python.
\entry*[Version Control]%
svn, git.
\entry*[Continuous Integration]%
 GitHub/GitLab, CircleCI, Docker.
\entry*[Languages]%
English (fluent), French (native speaker), German (scholar).
%
%
%
%
%
\pagebreak
\subrubric{Main Scientific Contributions}
\br\ms
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2016}$]%
- "Impact of Isotope Fidelity on Fuel Cycle Calculations" \textbf{B.~Mouginot,
P.P.H.~Wilson, R.W.~Carlsen}, \textit{Winter ANS 2016}, Las Vegas, U.S.A (11/2016) : oral presentation.
%
%
%
 \entry*[$\boldsymbol{2015}$]%
- "A neural network approach for burn-up calculation and its application to the dynamic fuel cycle code CLASS", \textbf{B.~Leniau, B.~Mouginot, T.~Thiolière \textit{et al.}}, \textit{Annals of Nuclear Energy}, 81, (2015).
%
%
%
%\vspace{0.05cm}
 \entry*[$\boldsymbol{2015}$]%
- "MOX fuel enrichment prediction in PWR using polynomial models",
\textbf{B.~Mouginot, B.~Leniau, T.~Thiolière \textit{et al.}}, \textit{Annals of Nuclear Energy},85 (2015).
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2014}$]%
- "Core Library Advanced Scenario Simulation, Principle \& Application." ~~~~~~~~~~~\textbf{B.~Mouginot, B.~Leniau, N.~Thiolière \textit{et al.}}, \textit{PHYSOR 2014}, Kyoto, Japon (09/2014) : poster.
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2013}$]%
- "CLASS : Core Library for Advanced Scenario Simulation." \textbf{B.~Mouginot, ~~~~~~~~~N.~Thiolière}, \textit{TCADS 2}, Nantes, France : oral presentation.
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2013}$]%
- "A high power ADS concept for the minor actinides transmutation." \textbf{N.~Thiolière, B.~Mouginot, J.B.~Clavel}, \textit{TCADS 2}, Nantes, France : oral presentation.
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2012}$]%
- "GEDEPEON Bilan" \textbf{B.~Mouginot, N.~Thiolière and J.B.~Clavel}, \textit{GEDEPEON}, Paris, France (décembre 2012) : oral presentation.
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2012}$]%
- "Lifetime measurement of 2+1 state in $^{74}$Zn by differential plunger method", \textbf{M.~Niikura, B.~Mouginot \textit{et al.}}, \textit{Physical Review C}, 85, (2012).
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2011}$]%
- "Search for the Giant Pairing Vibration through (p,t) reactions around 50 and ~~~~~~~~~~~~~~~~~60 MeV", \textbf{B.~Mouginot, E.~Khan, N.~Retief \textit{et al.}}, \textit{Physical Review C}, 83, (2011).
%
%
%
%\vspace{0.05cm}
\entry*[$\boldsymbol{2010}$]%
- "Exploring life-time of low-lying states in neutron rich nuclei towards $^{78}$Ni with the plunger technique at GANIL", \textbf{B.~Mouginot, M.~Niikura \textit{et al.}}, \textit{EURORIB'10}, Lamoura, France : oral presentation.
%
%
%
\vspace{0.05cm}
\entry*[$\boldsymbol{2008}$]%
- "Search of the Giant Pairing Vibration mode in nuclei", \textbf{B.~Mouginot, E.~Khan, R.~Neveling \textit{et al.}}, \textit{LEA COLLIGA Meeting}, Catane, Italie : oral presentation.
%
%
%
\entry*[$\boldsymbol{2008}$]%
- "Giant Pairing Vibrations: experimental overview", \textbf{B.~Mouginot, E.~Khan, ~~~~~~~R.~Neveling \textit{et al.}}, \textit{Probing pair correlations : experimental tools and associated models, Workshop}, Saclay, France : oral presentation.
\vspace{0.2cm}
%
%
%
%
%
\subrubric{Experimental Contributions}
 \br\ms
\entry*[$\boldsymbol{06/2009}$ and $\boldsymbol{10/2009}$]%
\textbf{Plunger experiment $^{74}$Zn}, GANIL, France : simulation, set-up, participation, online analysis and data analysis.
\entry*[$\boldsymbol{03/2009}$  and $\boldsymbol{03/2007} $]%
\textbf{GPV experiment}, iThemba LABS, South Africa : simulation, participation and data analysis.
\entry*[$\boldsymbol{09/2008}$]%
\textbf{Beam purification test at LISE line}, GANIL, France.
\entry*[$\boldsymbol{11/2007}$]%
\textbf{TIARA-MUST2-VAMOS-EXOGAM campaign}, GANIL, France : participation to $^{20}$O$(d,t)$ experiment and data analysis of the $^{36}$S$(d,t)/(d,^{3}$He$)$ test experiment.
\vspace{0.1cm}

\end{rubric}

